---
title: "<h1 style='text-align:center;'> Data handling tools </h1>"
author: "Hugo Marthinet"
date: "`r Sys.Date()`"
output:
  knitr:::html_vignette:
  toc: true
vignette: >
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteIndexEntry{Data handling tools}
  %\usepackage[utf8]{inputenc}
---

\setmainfont{Calibri Light}

```{r, echo = FALSE, message = FALSE}

# If you want to create a PDF document paste the following after line 9 above:
#   pdf_document:
#     toc: true
#     highlight: tango
#     number_sections: no
#     latex_engine: xelatex    
# header-includes: 
#    - \usepackage{fontspec}

knitr::opts_chunk$set(collapse = T, comment = "#>")
options(tibble.print_min = 4L, tibble.print_max = 4L)
library(lazyMe)
```

This packges provides coding shortcut to handle data before strating analysing it. 
Functions in the packages to not propose anything new, but merely grant an easy access to processes that would usualy require combination of 
several functions. This can be anything from the inverse of element testing (**is.na()**, **is.null()**...), vector handling (character, factor...)
or type conversion.

## Element testing

```{r, message = FALSE}
# Inverse of is.na()
x <- c(NA, NA, NA, "", NA, NA, NA, NA, "", NA, NA, NA, NA, "", NA, NA, NA, NA, "BATMAAAAAN")
is.na(x)
isnt.na(x)

# Inverse of %in%
x <- c("RiRi", "Fifi", "Loulou")
y <- c("Fifi", "Brindacier")
not.in(x, y)
x %ni% y

# Inverse of is.null()
a <- 1
b <- NULL
is.defined(a)
is.defined(b)
```

## Strings and factors

```{r, message = FALSE}
# Clean a string
str_clean("    bONjour & au Revoir    é     ")


# Index of pattern in a string
A <- "Une fois trois egal trois"
B <- "Deux fois trois egal six"

str_index(A, "trois")
str_index(A, "trois", mode = "premiere")
str_index(c(A, B), "trois")


# Relevel and set reference level of a factor
library(tab)
fac_race <- relevel_factor(fac = tabdata$Race,
               new.levels = list("White" = "Blanc", "Black" = "Noir", "Mexican American" = "Hispanique", "Other" = "Autre"),
               ref = "Autre")
head(fac_race)
```

## Type conversion

```{r, message = FALSE}
# Convert all of the columns of a given type in another one
head(iris)
iris2 <- convertAll(iris, "factor", "numeric")
str(iris2)


# Handle binary vector 
x <- sample(c("Yes", "No", "Maybe"), 25, replace = TRUE)
as.binary(x, true.val = "Yes")
```
